An Open Repository of Real-Time COVID-19 Indicators

### 2021-08-02 indicators/paper/paper.tex
Disambiguate the two ARs

% Please include corresponding author, author contribution and author declaration information
% Googlers: SA, SC, DCF, JG, KH, RH, PM, MPO, CS, BYS, BW, SW
\authorcontributions{Author contributions: A.R., L.B., M.J., A.R., J.T., A.C.,
  E.J.C., N.D., D.C.F., A.J.H., S.H., M.J., J.K., W.L.M.K., Z.C.L., L.M., N.L.O.,
  J.C.W., R.R., and R.J.T. obtained and managed data;
  A.R., J.B., J.F., Z.C.L., L.M., D.J.M., A.P., S.R., D.R., C.S., N.S., R.T.,
  V.V., L.W., B.W., J.C.W,, S.W., R.R., and R.J.T. designed software and
  research;
  A.R., L.B., M.J., A.R., J.T., W.A.S., T.A., A.B., J.B., L.B., A.A.C., A.C.,
  E.J.C., B.C., S.C., N.D., D.C.F., J.G., S.G., A.G., G.H., R.H., K.H., A.J.H.,
  S.H., M.J., A.J., J.K., A.K., M.X.L., L.M., K.M., D.J.M., B.N., M.P.O.,
  N.L.O., P.P., C.A.P., S.R., C.S., V.S., J.S., D.S., N.S., B.Y.S., V.S., S.T.,
  J.T., R.T., J.C.W., and R.J.T. developed software;
  S.A., W.A.S., A.C., B.C., D.C.F., S.G., G.H., K.M., D.J.M., B.N., C.S., J.S.,
  D.S., B.Y.S., and A.K.V.N. managed technical infrastructure and systems;
  A.R., L.B., M.J., A.R., J.T., J.B., A.C., E.J.C., N.D., D.C.F., A.G., K.H.,
  A.J.H., R.H., S.H., A.J., J.K., K.L., Y.J.L., Z.C.L., L.M., D.J.M., P.M., B.N.,
  N.L.O., P.P., C.A.P., S.R., N.S., V.S., J.S., D.S., N.S., S.T., J.T., R.T.,
  V.V., L.W., J.C.W., R.R., and R.J.T. performed research;
  R.R. and R.J.T. acquired funding;
  and A.R., L.B., M.J., A.R., J.T., and R.J.T. wrote the paper.
}
\authordeclaration{No competing interests to declare.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be
  addressed. E-mail: areinhar@stat.cmu.edu}
\equalauthors{\textsuperscript{2}L.B., M.J., A.R., and J.T. contributed equally
  to this work.}

>>>>

% Please include corresponding author, author contribution and author declaration information
% Googlers: SA, SC, DCF, JG, KH, RH, PM, MPO, CS, BYS, BW, SW
\authorcontributions{Author contributions: A.Re., L.B., M.J., A.Ru., J.T., A.C.,
  E.J.C., N.D., D.C.F., A.J.H., S.H., M.J., J.K., W.L.M.K., Z.C.L., L.M., N.L.O.,
  J.C.W., R.R., and R.J.T. obtained and managed data;
  A.Re., J.B., J.F., Z.C.L., L.M., D.J.M., A.P., S.R., D.R., C.S., N.S., R.T.,
  V.V., L.W., B.W., J.C.W,, S.W., R.R., and R.J.T. designed software and
  research;
  A.Re., L.B., M.J., A.Ru., J.T., W.A.S., T.A., A.B., J.B., L.B., A.A.C., A.C.,
  E.J.C., B.C., S.C., N.D., D.C.F., J.G., S.G., A.G., G.H., R.H., K.H., A.J.H.,
  S.H., M.J., A.J., J.K., A.K., M.X.L., L.M., K.M., D.J.M., B.N., M.P.O.,
  N.L.O., P.P., C.A.P., S.R., C.S., V.S., J.S., D.S., N.S., B.Y.S., V.S., S.T.,
  J.T., R.T., J.C.W., and R.J.T. developed software;
  S.A., W.A.S., A.C., B.C., D.C.F., S.G., G.H., K.M., D.J.M., B.N., C.S., J.S.,
  D.S., B.Y.S., and A.K.V.N. managed technical infrastructure and systems;
  A.Re., L.B., M.J., A.Ru., J.T., J.B., A.C., E.J.C., N.D., D.C.F., A.G., K.H.,
  A.J.H., R.H., S.H., A.J., J.K., K.L., Y.J.L., Z.C.L., L.M., D.J.M., P.M., B.N.,
  N.L.O., P.P., C.A.P., S.R., N.S., V.S., J.S., D.S., N.S., S.T., J.T., R.T.,
  V.V., L.W., J.C.W., R.R., and R.J.T. performed research;
  R.R. and R.J.T. acquired funding;
  and A.Re., L.B., M.J., A.Ru., J.T., and R.J.T. wrote the paper.
}
\authordeclaration{No competing interests to declare.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be
  addressed. E-mail: areinhar@stat.cmu.edu}
\equalauthors{\textsuperscript{2}L.B., M.J., A.Ru., and J.T. contributed equally
  to this work.}
